Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-19 main.tex
concerns

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, $C_0 \leq C_i$ for all $i<n$, where $C \leq
  C'$ if $\forall \component, C(\component) \leq C'(\component)$ and
  $\VIS < \HID$.

@@

  For each pair of traces in the hyperproperty, if the initial machine
  states plus contour are variants, then the observervations of the
  two traces coincide.

@@

>>>>

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, $C_0 \leq C_i$ for all $i<n$, where $C \leq
  C'$ if $\forall \component, C(\component) \leq C'(\component)$ and
  $\VIS < \HID$.
  \apt{Isn't this effectively still a negation in the functor? I thought for strategy for describing execution after a Return was to apply suffix closure to the original full trace -- but doesn't this criterion rule out the original full trace?}

@@

  For each pair of traces in the hyperproperty, if the initial machine
  states plus contour \apt{``elements''} are variants, then the observervations of the
  two traces coincide.

@@

\apt{Even if it works for subroutines,
  the basic idea of truncating traces when visibility increases doesn't 
  seem to extend to things like coroutines, where we swap between two sets of visible locations on each transfer.}
